Jug: Software for Reproducible Computation

### 2011-11-30 paper.tex
TXT+BIB Add new ref. Compare to it

@@

Figure~\ref{fig:jug-shell-interaction} shows a possible interaction session
with jug shell. While having to explicitly load all the results is a bit
bothersome, it has some advantages versus the alternative of pre-loading all.
It is much faster at startup. Consider too that the user might not load more
than a few objects. In some cases, loading all of the objects simultaneously
might even be impossible due to memory constraints. Further, this allows
exploration of the task structure for debugging.

>>>>

\citet{Fomel2007} proposed a system built on top of Scons which shared
superficially similar design. Scons, like Make, is a build system. It supports
spawning parallel jobs using multiple threads. In the original use case, the
tasks are delegated to other commands and the operating system can take care of
parallelism. If, however, the tasks are computationally intensive in Python,
contention for the global interpreter lock will limit the amount of real
parallelism.\footnote{In the most commonly used Python interpreters, there is a
lock that prevents more than one thread from simultaneously executing
interpreted code, although they can execute non-interpreted code, as calling an
external programme or certain external libraries.}

@@

Figure~\ref{fig:jug-shell-interaction} shows a possible interaction session
with jug shell. While having to explicitly load all the results is a bit
bothersome, it can be better than pre-loading all of them. It is much faster at
startup. Consider too that the user might not load more than a few objects. In
some cases, loading all of the objects simultaneously might even be impossible
due to memory constraints. Further, this allows exploration of the task
structure for debugging.
